---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# flowers
<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/flowers)](https://CRAN.R-project.org/package=flowers)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

Flowers is a package for generating flower plots.  It was derived from code
from Jim Regetz at NCEAS, and then rewritten and extended by the OHI project.
This package formalizes the approach into an easily re-usable function
for generating custom flower plots for multiple scenarios.

## Quick Start

This is a basic example which shows you how to create a flower plot from an 
appropriately structured data set:

```{r example, fig.width=8, fig.height=8, out.width="70%"}
library(flowers)
data(ohi)
plot_flower(ohi, "OHI Example Flower")
```

Currently `plot_flower()` expects particular column names and semantics, but
this could be made more flexible.  See the structure of OHI for an example.

```{r ohi_structure, echo=FALSE}
str(ohi)
```

## Installation

You can install the development version of flowers from [GitHub](https://github.com/mbjones/flowers) with:

``` r
devtools::install_github("mbjones/flowers")
```

You can install the released version of flowers from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("flowers")
```
